---
title: " Tooth Growth Data Inferential Analysis"
author: "Shivam Giri"
date: "August 30, 2017"
output: pdf_document
---
## Data Preprocessing 
```{r setup}
library(datasets)
data("ToothGrowth")

```


## Exploratory Data Analysis
```{r}

str(ToothGrowth)
summary(ToothGrowth)
levels(ToothGrowth$supp)<-c("Orange juice","Vitamin C")

library(ggplot2)

ggplot(data = ToothGrowth,aes(x=factor(dose),len,fill=factor(dose)))+geom_boxplot()+facet_grid(facets = .~supp)+labs(title="Tooth Growth Variation",x="Dose",y="Tooth Length")
```

## Statistical Tests and Inference

### Hypothesis 1
Both Orange Juice and Vitamin C enables equal tooth growth for all doses
```{r}
hypo1<-t.test(len~supp,ToothGrowth)
hypo1$conf.int
hypo1$p.value

```
The confidence intervals include 0 and the p-value is greater than the threshold of 0.05. The null hypothesis cannot be rejected.



### Hypothesis 2
Both Orange Juice and Vitamin C enables equal tooth growth for dose = 0.5 mg/day
```{r}
hypo2<-t.test(len~supp,ToothGrowth,dose==0.5)
hypo2$conf.int
hypo2$p.value
```
The confidence interval does not include 0 and the p-value is below the 0.05 threshold. The null hypothesis can be rejected.


### Hypothesis 3
Both Orange Juice and Vitamin C enables equal tooth growth for dose = 1.0 mg/day
```{r}
hypo3<-t.test(len~supp,ToothGrowth,dose==1.0)
hypo3$conf.int
hypo3$p.value
```
The confidence interval does not include 0 and the p-value is smaller than the 0.05 threshold. The null hypothesis can be rejected. 



### Hypothesis 4
Both Orange Juice and Vitamin C enables equal tooth growth for dose = 2.0 mg/day
```{r}
hypo4<-t.test(len~supp,ToothGrowth,dose==2.0)
hypo4$conf.int
hypo4$p.value
```
The confidence interval does include 0 and the p-value is larger than the 0.05 threshold. The null hypothesis cannot be rejected.



## Conclusion
AS evident from above hypotheses, for dosages of 0.5 and 1.0 mg/day, tooth growth occurs more in the case of Orange Juice than Vitamin C.

In the case of dose of 2.0 mg/day, equal tooth growth can be said to be achieved with p-value equal to 0.96

